Fourmile state variables

### 2025-05-02 state_vars.Rmd
adding burn & unburn HRU examples

# 2015 for low and high HRU

@@

# ANOVA for water partition

@@

flow <- both %>%
  select(date, 
         source, 
         outRG1,
         outRG2,
         outRD1, 
         outRD2,
         source)

rd1_model <- aov(outRD2 ~ source, data = flow)
summary(rd1_model)

>>>>

# 2016 for low and high HRU

@@

# Burn vs Unburn HRU

@@

unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'unburn') %>%
  filter(year == 2016)

burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'burn') %>%
  filter(year == 2016)
